Experimental Analysis of a Spatialised Audio Interface for People with Visual Impairments

### 2020-05-15 review/response/response.tex

\author{J.C. Lock; I.D. Gilchrist; G. Cielniak; N. Bellotto}

\maketitle

\noindent Dear associate editors and reviewers,

We would first like to sincerely thank you all for taking the time for reviewing our work and for your honest and helpful feedback.
We have taken some time to go over and implement your suggestions and we believe that we can resubmit to you an improved version of the paper. 
Please find below our responses to your comments and suggestions, where we point out how we addressed them.

@@

\section*{Reviewer 1}

\begin{itemize}
  \item R1.1 \textit{However, the paper should be thoroughly proofread as there are a number of typos}
  \item[] Thank you for pointing these out. We have proofread the paper and amended all typos.

  \item R1.2 \textit{The references are generally appropriate. However, additional details on the problem and literature references would be useful (a number of seminal, updated and novel works are below). In particular, the claim that "...both haptic and vocal feedback can present a cognitive burden and overwhelm a user’s input bandwidth, particularly when high-resolution guidance is required." needs to be clarified.
      In essence, as suggested in [kammoun2012navigation,petrie1997mobic], there are two synergic classes of information to be conveyed: directions (or macro-navigation), which is commonly conveyed through turn-by-turn instructions (e.g., [sato2019navcog3]), and space-related information (or micro-navigation), which is better conveyed through spatialized audio.
      Indeed, Arditi and Tian refer to the task of "request information about environmental objects", which is a micro-navigation task, and for which the participants preferred on-demand information rather than continuous feedback.
In this frame, the proposed analysis of the performance in localizing spatialized sound for micro navigation tasks using bone-conducting headphones is useful since many works already use bone conducting headphones for guidance, but their accuracy still needs to be validated.
}
  \item[] Thank you for the suggestions.
    To address these concerns, we have added additional information to the Introduction (Section 1) that frames this as a micro-navigation task.
    We have also added an additional reference at the line in question to support our argument for not using constant vocal or haptic feedback such a micro-navigation task context.
    We also added the works the reviewer kindly provided in the Previous Work (Section 2).

  \item R1.3 \textit{The authors published an initial paper on the system. With respect to that paper, here the experiments are extended, including also an analysis of the time-to-target fitting with respect to Fitts's Law.
    While the amount of novel content seems to be appropriate for a journal extension of the paper, the system description is copied verbatim from the previous paper, and Figures 1b, 2 and 3 are essentially identical. Content provided elsewhere should be summarized and readapted and not copied.}
  \item[] Thank you for pointing this out.
    To address this, we have completely rewritten the System Description (Section 3) and further modified the figures in question (see Fig. 1).

### 2020-05-15 review/response/response.tex

\end{itemize}

\section*{Reviewer 2}

\begin{itemize}

  \item R2.1 \textit{The authors might make mention of the Microsoft Soundscape system. While this system does not provide information about elevation, it is an example of a commercially available navigation aid that uses spatialized audio. https://www.microsoft.com/en-us/research/product/soundscape/. While I have reservations about using Fitts’s Law in this paper, probably the single best citation for the justification for using We is [zhai2004]. Also not all that critical given my reservations, but JFYI. In two-dimensional directed pointing, the calculation of We is better calculated as described in [wobbrock2011]}
  \item[] We'd like to thank the reviewer for these helpful references. 
    We have added the reference from~\cite{zhai2004speed}, as well as a paper by~\cite{kabbash1995prince}, in Section 4.3 to support our use of $w_e$ in this work.
    We have also revised the way we calculate $w_e$ based on the recommendations from the reviewer and~\cite{wobbrock2011effects} recommendations and made mention of this in Section 4.3. 
    These changes have led to modifications to Fig. 11 and 12 and have improved the overall model fit.
    The updated results are discussed in Sections 5.4 and 5.5 and listed in Table 4.

@@

  \item R2.4 \textit{And, as seen in Fig 8, there are huge differences in the distribution of ``error'' between the two groups (G1 \& G2), and I suspect there may be even larger differences between users: different thresholds of ``good enough'' for different users. It’s also not clear to me if We is calculated for each level of Distance, or is it calculated across multiple amplitude of movements?}
  \item[] As mentioned in R2.3, the thresholds of `good enough' is this experiment's measurement.
    However, to address the reviewer's concerns and clarify our method, we have added additional details in Section 4.3 of how we determined $w_e$ and use it to determine a setting's expected performance. 
    In summary, we calculated a $w_e$ for each participant's experiment run and used the median of all the participants to fit the curves in Fig 11 and generate the $IP$ in Fig 12.

  \item R2.5 \textit{So my skepticism of the whole exercise of using Fitts’s Law for comparing these conditions is that it feels weird to me to reconstitute some form of W (We) from the spread of hits around a point target when there’s no objective feedback for hitting it (i.e., no W). Since they mostly just use this to make comparisons between different elevation stimuli, it’s not clear that they NEED to do this anyway. I think they could probably just use speed \& distance and be done with it, especially since there is no change in W. I guess if We were actually changing with different conditions (D or elevation), there might be some justification for this (though We in that case will be highly correlated with D, which would violate at least the spirit of the law), but this experiment seems way too small to detect this (and this detail isn’t reported anyway). Why go to all the trouble of doing the Fitt’s analysis when the only thing you’re varying is distance? Indeed, for the final take-aways that the authors provide, this seems like enormous overkill.}
  \item[] We'd like to thank the reviewer for this feedback.
    To address these concerns, we have added text in Section 1, where additional context behind the reason for these experiments and how their results will be used is provided. 
    In summary, for this project we were looking into ways to automate an optimisation process where an audio interface changes its own audio parameters to boost the user's target-finding performance.
    For this, we required a robust model that can provide a quantifiable measure of performance (Fitts Index of Performance).
    %At the time this work was conducted, it was not clear that Fitts's model could provide us with a useful measure based on the literature we had at hand and is the main reason we conducted this analysis.
    We acknowledge the reviewer's valid comment about not strictly conforming to the law and we amended the wording in the Introduction (Section 1) to use less absolute language and say that we found that the interface `exhibits a response that is well-modelled by Fitts’s Law'  instead of `conforms to Fitts's Law'.

### 2020-05-15 paper.tex
Updated response, added participant table, adapted figures
Minor changes to figure 1
Fixed American spelling, checked spelling elsewhere

\begin{figure}
  \centering
  %\subfloat[]{\label{fig:tango-headphone}\includegraphics[width=0.5\columnwidth]{figures/tango_tablet_headphone_edit.pdf}}
%~
  %\subfloat[]{\label{fig:participant}\includegraphics[width=0.8\columnwidth]{figures/vi_participant_e.png}}
  \includegraphics[width=0.8\columnwidth]{figures/vi_participant_e.png}
  \caption{The Tango tablet and bone-conduction headphones in use during an experiment. The angle reference system that the guidance instructions are based on is also included , showing the camera vector, $C$, and the pan and elevation angles to the target. Adapted from~\citet{lock2019bone}.}\label{fig:participant}
  \Description{The Tango tablet and the bone-conduction headphones, the primary hardware components used in this work, and a participant with visual impairments using the system during an experiment.}
\end{figure}

@@

\hl{Over the years, commercial and academic groups have devised new and innovative mobile navigation and travel aids for people with visual impairments to address macro- and micro-navigation issues.
  The latter refer to the scale that navigation takes place on, with macro-navigation addressing directional guidance on a topographical map using turn-by-turn instructions, for example, while micro-navigation focusses on conveying information of the user's immediate surroundings~\citep{petrie1997mobic}. 
Many of the proposed systems make use of one or a combination of vocal~\citep{mocanu2016when,chessa2016integrated,kanwal2015navigation,sato2019navcog}, audio~\citep{schwarze2015intuitive,rodriguez2012obstacle,kammoun2012navigation} and haptic~\citep{rivera-rubio2015assistive,lee2015rgb,xiao2015assistive} feedback media to present a user with macro- and/or micro-guidance instructions, each of which has its own set of features and limitations.
The interface for this work is used to provide instructions to a stationary user to guide them to point a camera at a target location and we therefore are mainly concerned with micro-navigation tools. 
In this context, respondents with visual impairments typically prefer haptic and vocal feedback over an audio tone~\citep{arditi2013user,golledge2004stated}.
However, from an ergonomic perspective, haptic feedback has significant shortcomings and require additional external hardware to transmit guidance instructions with sufficient resolution.
Furthermore, in a micro-navigation task, high-resolution guidance and many adjustments are required to reach the target location.
This this regard, both haptic and vocal feedback can present a cognitive burden and overwhelm a user's input bandwidth, which could have a detrimental effect on performance and the user experience~\citep{klatzky2006cognitive}.}
%Indeed, \citet{arditi2013user} reports that users prefer controlling the rate at which guidance signals are presented to them, instead of being given constant guidance. 
As an alternative, simple audio tones are less prone to these bandwidth and hardware limitations.
However, such tones can potentially fatigue a user if there are too unpleasant.
Researchers have started using cameras and object detectors to determine what a user is looking at and then use simple audio tones and vocal feedback signals to indicate to the user where to find an object.
They report favourable results with these systems~\citep{schauerte2012assistive,tian2013computer,fiannaca2014headlock,vazquez2012helping}.

@@

For this progressive increase in difficulty, a ``2-up, 1-down'' step process is used~\citep{wetherill1965sequential,levitt1971transformed}, meaning that for every two correct answers, the distance to the centre halves.
Conversely, the task becomes easier for each incorrect answer by doubling the sound source's distance from the centre.
We also use two different step sequences, one starting at a large angular distance (\SI{45}{\degree}) from the user and the other at the minimum distance (approximately \SI{1}{\degree}), giving an `easy' and a `hard' progression respectively.
The terminating condition for the experiment is when the two sequences converge to within two intervals of one another for three consecutive guesses.
For example, the experiment will terminate when one sequence is set to \SI{11.25}{\degree} and the other is between \SI{2.8}{\degree} or \SI{45}{\degree} for three consecutive guesses.
This gives a distance band where the participant is capable of localizing the sound source.
Each participant performed this experiment three times.

@@

In this paper we investigated the use of spatialised audio interface with varying pitch to guide a user with visual impairments in a target pointing task.
We found that the blindfolded participants and those with severe sight impairments performed similarly in localizing sound sources and differentiating between tones. 
We also found that both groups were able to find a randomly distributed set of virtual targets with similar levels of accuracy.
However, the blindfolded group outperformed the one with severe sight impairments in terms of time-to-target. 
We further tested different pitch settings and found that the user performance in the pan dimension, based on spatialised cues, is independent of such settings.
Moreover, we noticed a speed/accuracy trade-off between the settings, where a higher pitch setting produces a smaller angular error, but at the cost of reducing the time performance (i.e.\ more time to reach the target). 
These results, together with an analysis done with Fitts's Law that confirms its applicability to this type of audio interface, provide a useful baseline to improve and refine the latter in future applications, prioritising speed or accuracy to produce the desired output.

>>>>

\begin{figure}
  \centering
  %\subfloat[]{\label{fig:tango-headphone}\includegraphics[width=0.5\columnwidth]{figures/tango_tablet_headphone_edit.pdf}}
%~
  %\subfloat[]{\label{fig:participant}\includegraphics[width=0.8\columnwidth]{figures/vi_participant_e.png}}
  \includegraphics[width=0.65\columnwidth]{figures/vi_participant_e.png}
  \caption{The Tango tablet and bone-conduction headphones in use during an experiment. The angle reference system that the guidance instructions are based on is also included , showing the camera vector, $C$, and the pan and elevation angles to the target. Adapted from~\citet{lock2019bone}.}\label{fig:participant}
  \Description{The Tango tablet and the bone-conduction headphones, the primary hardware components used in this work, and a participant with visual impairments using the system during an experiment.}
\end{figure}

@@

\hl{Over the years, commercial and academic groups have devised new and innovative mobile navigation and electronic travel aids (ETA) for people with visual impairments to address macro- and micro-navigation issues.
  The latter refer to the scale that navigation takes place on, with macro-navigation addressing directional guidance on a topographical map using turn-by-turn instructions, for example, while micro-navigation focusses on conveying information of the user's immediate surroundings~\citep{petrie1997mobic}. 
Many of the proposed systems make use of one or a combination of vocal~\citep{mocanu2016when,chessa2016integrated,kanwal2015navigation,sato2019navcog}, audio~\citep{schwarze2015intuitive,rodriguez2012obstacle,kammoun2012navigation} and haptic~\citep{rivera-rubio2015assistive,lee2015rgb,xiao2015assistive} feedback media to present a user with macro- and/or micro-guidance instructions, each of which has its own set of features and limitations.
The interface for this work is used to provide instructions to a stationary user to guide them to point a camera at a target location and we therefore are mainly concerned with micro-navigation tools. 
In this context, respondents with visual impairments typically prefer haptic and vocal feedback over an audio tone~\citep{arditi2013user,golledge2004stated}.
However, from an ergonomic perspective, haptic feedback has significant shortcomings and require additional external hardware to transmit guidance instructions with sufficient resolution.
Furthermore, in a micro-navigation task, high-resolution guidance and many adjustments are required to reach the target location.
This this regard, both haptic and vocal feedback can present a cognitive burden and overwhelm a user's input bandwidth, which could have a detrimental effect on performance and the user experience~\citep{klatzky2006cognitive}.}
%Indeed, \citet{arditi2013user} reports that users prefer controlling the rate at which guidance signals are presented to them, instead of being given constant guidance. 
As an alternative, simple audio tones are less prone to these bandwidth and hardware limitations.
However, such tones can potentially fatigue a user if there are too unpleasant.
Researchers have started using cameras and object detectors to determine what a user is looking at and then use simple audio tones and vocal feedback signals to indicate to the user where to find an object.
They report favourable results with these systems~\citep{schauerte2012assistive,tian2013computer,fiannaca2014headlock,vazquez2012helping}.

@@

For this progressive increase in difficulty, a ``2-up, 1-down'' step process is used~\citep{wetherill1965sequential,levitt1971transformed}, meaning that for every two correct answers, the distance to the centre halves.
Conversely, the task becomes easier for each incorrect answer by doubling the sound source's distance from the centre.
We also use two different step sequences, one starting at a large angular distance (\SI{45}{\degree}) from the user and the other at the minimum distance (approximately \SI{1}{\degree}), giving an `easy' and a `hard' progression respectively.
The terminating condition for the experiment is when the two sequences converge to within two intervals of one another for three consecutive guesses.
For example, the experiment will terminate when one sequence is set to \SI{11.25}{\degree} and the other is between \SI{2.8}{\degree} or \SI{45}{\degree} for three consecutive guesses.
This gives a distance band where the participant is capable of localising the sound source.
Each participant performed this experiment three times.

@@

In this paper we investigated the use of spatialised audio interface with varying pitch to guide a user with visual impairments in a target pointing task.
We found that the blindfolded participants and those with severe sight impairments performed similarly in localising sound sources and differentiating between tones. 
We also found that both groups were able to find a randomly distributed set of virtual targets with similar levels of accuracy.
However, the blindfolded group outperformed the one with severe sight impairments in terms of time-to-target. 
We further tested different pitch settings and found that the user performance in the pan dimension, based on spatialised cues, is independent of such settings.
Moreover, we noticed a speed/accuracy trade-off between the settings, where a higher pitch setting produces a smaller angular error, but at the cost of reducing the time performance (i.e.\ more time to reach the target). 
These results, together with an analysis done with Fitts's Law that confirms its applicability to this type of audio interface, provide a useful baseline to improve and refine the latter in future applications, prioritising speed or accuracy to produce the desired output.
